---
title: "Lab 06"
author: "Jaxon Abercrombie"
date: "10/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidytext)

```

## Download the Data
```{r get-data}
fn <- "mtsamples.csv"
if (!file.exists(fn))
  download.file("https://raw.githubusercontent.com/USCbiostats/data-science-data/master/00_mtsamples/mtsamples.csv", destfile = fn)

library(tibble)

mtsamples <- read.csv(fn)
mtsamples <- as_tibble(mtsamples)
mtsamples

```

## Q1: How many and how are specialties distributed?
```{r dist-of-specialties}
specialties <-
  mtsamples %>%
  count(medical_specialty)

specialties %>%
  arrange(desc(n)) %>%
  top_n(n, 15) %>%
  knitr::kable()
```

There are `r nrow(specialties)` specialties. Let's take a look at the distribution:

```{r dist}
#Method 1 (not that pretty)
mtsamples %>%
  ggplot(aes(x = medical_specialty)) +
  geom_histogram(stat = "count") +
  coord_flip()

#Method 2
library(forcats)
ggplot(specialties, aes(x = n, y = fct_reorder(medical_specialty, n))) +
  geom_col()

```

```{r dist2}
mtsamples %>%
  ggplot(aes(x = medical_specialty)) +
  geom_histogram(stat = "count") +
  coord_flip()
```

These are not evenly (uniformly) distributed.

## Q2
```{r imp-words}
library(tidytext)
mtsamples %>%
  unnest_tokens(output = word, input = transcription) %>%
  count(word, sort = TRUE) %>%
  # Using regular expressions to remove numbers
  anti_join(stop_words, by = "word") %>%
  filter(!grepl(pattern = "^[0-9]+$", x = word)) %>%
  top_n(20) %>%
  ggplot(aes(x = n, y = fct_reorder(word,n))) +
    geom_col()
```

The word "patient" appears to be important (of course!), but we observe many stopwords.

#Q3
```{r imp-words2}
mtsamples %>%
  unnest_tokens(output = word, input = transcription) %>%
  count(word, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(x = n, y = fct_reorder(word,n))) +
    geom_col()
```

Looking better, but we do not like the numbers.

#Q4
```{r imp-words3, cache = TRUE}
mtsamples %>%
  unnest_ngrams(output = trigram, input = transcription, n = 3) %>%
  count(trigram, sort = TRUE) %>%
  top_n(20) %>%
  ggplot(aes(x = n, y = fct_reorder(trigram,n))) +
    geom_col()
```

Using bi-grams is not very informative, so let's try tri-grams.